\small
\begin{thebibliography}{MMMM}
    \itemsep=-.5ex
    
    \bibitem[Be07]{bergner} Julia E. Bergner (2007).
    A model category structure on the category of simplicial categories.
    \emph{Transactions of the AMS} \textbf{359}, 2043--2058.

    \bibitem[DK80a]{dk-loc} W.\,G. Dwyer and D.\,M. Kan (1980).
    Simplicial Localizations of Categories.
    \emph{Journal of Pure and Applied Algebra} \textbf{17}, 267--284.

    \bibitem[DK80b]{dk-calc} W.\,G. Dwyer and D.\,M. Kan (1980).
    Calculating Simplicial Localizations.
    \emph{Journal of Pure and Applied Algebra} \textbf{18}, 17--35.

    \bibitem[Hi13]{hinich13} Vladimir Hinich.
    \emph{Dwyer--Kan Localization Revisited}. arXiv:1311.4128.

    \bibitem[Hi17]{hinich} Vladimir Hinich.
    \emph{Lectures on Infinity Categories}. arXiv:1709.06271.

    \bibitem[Ho99]{hovey} Mark Hovey (1999).
    \emph{Model Categories}. 
    Mathematical Surveys and Monographs \textbf{63}. AMS.

    \bibitem[HoTT]{hott} The Univalent Foundations Program (2013).
    \emph{Homotopy Type Theory}.    

    \bibitem[Lu09]{htt} Jacob Lurie (2009).
    \emph{Higher Topos Theory}. 
    Annals of Mathematics Studies \textbf{170}. Princeton University Press.

    \bibitem[Lu]{ha} Jacob Lurie.
    \emph{Higher Algebra}. Preprint.

    \bibitem[Ma99]{may} J.\,P. May (1999).
    \emph{A Concise Course in Algebraic Topology}.
    Chicago Lectures in Mathematics.
    University of Chicago Press.

    \bibitem[ML98]{maclane} Saunders Mac Lane (1998).
    \emph{Categories for the Working Mathematician}.
    Graduate Texts in Mathematics \textbf{5}. Springer.

    \bibitem[Qu67]{quillen} Daniel G. Quillen (1967).
    \emph{Homotopical Algebra}.
    Lecture Notes in Mathematics \textbf{43}. Springer.

    \bibitem[Ri]{riehl} Emily Riehl.
    Homotopy (Limits and) Colimits.

    \bibitem[RV]{elements} Emily Riehl and Dominic Verity.
    \emph{Elements of $\infty$-Category Theory}. Preprint.

    \bibitem[Ta05]{tabuada} Gonçalo Tabuada (2005).
    Une structure de catégorie de modèles de Quillen sur la catégorie des dg-catégories.
    \emph{Comptes Rendus Mathématique} \textbf{340} (1), 15--19.

    \bibitem[We95]{weibel} Charles A. Weibel (1995).
    \emph{An Introduction to Homological Algebra}.
    Cambridge Studies in Advanced Mathematics \textbf{38}.
    Cambridge University Press.
\end{thebibliography}
